
\iffalse
\documentclass[12pt]{llncs}

\usepackage{todonotes}

\usepackage{nla} 

\begin{document}
\fi

\title{Optimality conditions for nonlinear\\ measure-driven processes\thanks{The research is carried out within the framework of the state assignment of the Ministry of Education and Science of Russia for the project ``Theory and methods for studying  of evolutionary equations and control systems with applications,'' no.~121041300060-4.
}
}

\author{Vladimir Dykhta \and Olga Samsonyuk \and
 Stepan Sorokin \and
 Maksim Staritsyn
%  \and
%  Name FamilyName2\inst{2}
%  \and
%  Name FamilyName3\inst{1}
}
\institute{Matrosov Institute for System Dynamics and Control Theory
	of SB RAS, Irkutsk, Russia\\
  \email{dykhta@gmail.com, olga.samsonyuk@icc.ru, sorsp@mail.ru, starmax@icc.ru}
%  \and
%Affiliation, City, Country\\
%\email{email@example.com}
}

\maketitle

\begin{abstract}
This talk addresses optimal impulsive control problems for nonlinear differential equations driven by vector-valued Borel measures. We propose necessary and sufficient optimality conditions based on special functions of the Lyapunov type. These functions possess the property of strong and weak monotonicity with respect to the impulsive control system.

\keywords{optimal control, impulsive control, measure differential equations, feedback control, optimality conditions}
\end{abstract}



We consider a broad class of optimal control problems for nonlinear measure-driven equations. For such problems, we propose ne\-ces\-sa\-ry and sufficient optimality conditions generated by certain functions of the Lyapunov type and discuss some perspectives of designing  nonlocal numeric algorithms for optimal impulsive control \cite{nlaDykh2022,nlaDykh2016,nlaDykhSam2018IFAC,nlaSam2020JOGO,nlaSamSorStar2019,nlaSamSorStar2019Motor}.  
%We offer the notion of strongly and weakly monotone functions with respect to a measure-driven differential equation, and give constructive monotonicity criteria. 
%The sufficient conditions are formulated by sets of weakly or strongly monotone functions that are independent of the reference process and specify some estimates of the reachability set. Necessary 
%The optimality conditions operating with a specific class of impulsive feedback controls. These feedback controls are constructed in a way similar to the dynamical programming, but with the use of weakly monotone solutions to the corresponding Hamilton-Jacobi equation, instead of the Bellman's function. 
%Based on a space-time representation of impulsive processes, we propose the concept of impulsive feedback control and present   nonlocal necessary optimality conditions, which are shown to filter out non-optimal extrema of the impulsive Maximum Principle.


  

\begin{thebibliography}{9} 

\bibitem{nlaDykh2022} Dykhta~V.A. On the set of necessary optimality conditions with positional controls generated by weakly decreasing solutions to the Hamilton-Jacobi inequality. Proceedings of Krasovskii Institute of Mathematics and Mechanics UB RAS. 2022. T.~28, \textnumero~3. Pp.~83--93.

\bibitem{nlaDykh2016}  Dykhta~V.A.  Positional Strengthenings of the Maximum Principle and Sufficient Optimality Conditions. Proc. Steklov Inst. Math. (Suppl.) 2016. Vol.~293, suppl. 1. Pp. 43--57.

\bibitem{nlaDykhSam2018IFAC}
Dykhta~V.A., Samsonyuk~O.N. 
Optimality Conditions with Feedback Controls for Optimal Impulsive Control Problems. 
IFAC-Papers OnLine. 2018. Vol.~51, No.~32. Pp.~509--514.
%\url{https://doi.org/10.1016/j.ifacol.2018.11.472}  

\bibitem{nlaSam2020JOGO}
Samsonyuk~O.N. 
Optimality Conditions for Optimal Impulsive Control Problems with Multipoint State Constraints. Journal of Global Optimization. 2020. Vol.~76, No.~3. Pp.~625--644. 
%\url{https://doi.org/10.1007/s10898-019-00868-w}

\bibitem{nlaSamSorStar2019}
Samsonyuk~O., Sorokin~S., Staritsyn~M.
Feedback Necessary Optimality Conditions for Nonlinear Measure-Driven Processes. 
IFAC-Papers OnLine. 2019. Vol.~52, No.~16. Pp.~132--137.
%\url{https://doi.org/10.1016/j.ifacol.2019.11.767}


\bibitem{nlaSamSorStar2019Motor}
Samsonyuk~O., Sorokin~S., Staritsyn~M.
Feedback Optimality Conditions with Weakly Invariant Functions for Nonlinear Problems of Impulsive  Control. Proc. of the 18th International Conference ``Mathematical Optimization Theory and Operations Research'' (MOTOR-2019). Ekaterinburg, Russia, July 8--12, 2019. Lecture Notes in Computer Science. Cham: Springer, 2019. Vol.~11548. 
Pp.~513--526.
%\url{https://doi.org/10.1007/978-3-030-22629-9_36}


\end{thebibliography}
%\end{document}
