
\iffalse
\documentclass[12pt]{llncs}

\usepackage{todonotes}

\usepackage{nla} 

\begin{document}
\fi

\title{On embedding of Morse-Smale diffeomorphisms in topological flows\thanks{The research is supported by   Basic Research Program at the National Research University Higher School of Economics (HSE University).}}

\author{Elena Gurevich
  }
\institute{NRU HSE, Nizhnii Novgorod, Russia\\
  \email{els93@yandex.ru}
  }

\maketitle

\begin{abstract}
J.~Palis found necessary  conditions for  a Morse-Smale diffeomorphism on a closed $n$-dimensional manifold $M^n$  to  embed into a topological  flow and proved that these conditions are also sufficient for $n=2$ (see [1]).  For the case $n=3$ a possibility of  wild embedding of closures of separatrices of saddles is an additional obstacle  for Morse-Smale cascades to embed into topological flows. A criterion for Morse-Smale diffeomorphisms on  3-dimensional manifolds to embed into a topological  flow is obtained in~[2].    In [3] it is proved that if $M^n$ is homeomorphic to sphere $S^n$ of dimension $n\geq 4$ and a Morse-Smale diffeomorphism $f: M^n\to M^n$  have no  heteroclinic intersections, then $f$ embeds in a topological flow if and only if its non-wandering set consists of fixed points. In the report, we discuss new surprising obstructions  to embedding in  a flow,  and solution of the problem, for  Morse-Smale diffeomorphisms with locally flat closures of separatricies,  given on  manifolds of dimension $n\geq 4$.  

\keywords{embedding diffeomorphism into a flow,  Morse-Smale diffeomorphism and flows, wild separatricies, topological classification}
\end{abstract}


\begin{thebibliography}{9} % or {99}, if there is more than ten references.
\bibitem{1} J. Palis.  On Morse-Smale dynamical systems. Topology. 1969. Vol.~8, no~4. Pp.~385--404.

\bibitem{2} V. Z. Grines, E. Ya. Gurevich, V. S. Medvedev, O. V. Pochinka. On embedding a Morse-Smale diffeomorphism on a 3-manifold in a topological flow.  Sb. Math. 2012. Vol.~203, no.~12. Pp.~1761--1784.

\bibitem{3} V. Grines, E. Gurevich, O. Pochinka.   On Embedding of Multidimensional Morse-Smale Diffeomorphisms into Topological Flows.  Moscow Mathematical Journal. 2019. Vol.~19, no.~4. Pp.~739-760.

\end{thebibliography}
%\end{document}
