
\iffalse
\documentclass[12pt]{llncs}

\usepackage{todonotes}

\usepackage{nla} 

\begin{document}
\fi

\title{Asymptotic behavior of solutions to a linear delay differential equation\thanks{This work was supported by the Mathematical Center in Akademgorodok, Agreement No. 075-15-2022-282 with the Ministry of Science and Higher Education of the Russian Federation.}}
% First author
\author{Ivan~D.~Ilyinykh}
\institute{Novosibirsk State University, Novosibirsk, Russia\\
\email{i.ilinykh@g.nsu.ru}}

\maketitle

\begin{abstract}
  We consider solutions to a linear delay equation,
	as well as their relation 
  with the last components of solutions to high-dimensional 
  systems of ordinary differential equations. The aim of 
  the work is to obtain estimates for the convergence rate 
  of solutions to the delay equation
	to zero as $t \to \infty$. 
  To achieve this, stability regions of the zero solution to 
  corresponding systems are investigated 
  and a sequence of Lyapunov equations is solved.
  
  \keywords{delay equation, stability, Lyapunov equation, matrix spectrum} % No period at the end of the list
\end{abstract}

Consider the following delay differential equation
$$
\frac{dy(t)}{dt} = ay(t) + by(t-\tau), \quad t > 0,
\eqno (1)
$$
where $a, b, \tau \in \mathbb{R}$ are constants, $\tau > 0$. Consider also a sequence of high-dimensional systems of ordinary differential equations
$$
\frac{dx(t)}{dt} = A_nx(t),
\eqno (2)
$$
where 
$$
A_n = \left(
\begin{array}{ccccc}
-\frac{n-1}{\tau} & 0 & \ldots & \ldots & b\\
\frac{n-1}{\tau} & -\frac{n-1}{\tau} & \ddots & \ddots & 0\\
0 & \ddots & \ddots & \ddots & \vdots\\
\vdots & \ddots & \ddots & -\frac{n-1}{\tau} & 0\\
0 & \ldots & 0 & \frac{n-1}{\tau} & a
\end{array}
\right),
\quad
x(t) = \left(
\begin{array}{c}
x_1(t)\\
x_2(t)\\
\vdots\\
x_n(t)
\end{array}
\right).
%\eqno (3)
$$

It should be noted that G.V.~Demidenko established connections
between solutions to some classes  of nonlinear systems
of ordinary differential equations of large dimensions and solutions
to delay differential equations (see, for, example, [1--3]).

We define regions of the asymptotic stability of the zero solutions to 
(1) and (2) in the parameter space $(a, b)$. We 
establish that, for any $n \geq 2$, 
the regions of the asymptotic stability for (2) contain 
the region of the asymptotic stability for 
(1) and converge to it as $n \to \infty$. Solutions 
to Lyapunov equations for (2) are found; moreover, we define a limit 
function to which they converge as $n \to \infty$.

% At the end of the text, acknowledgments are expressed, if you haven't
% made a footnote from the title. For example, we can write

\begin{thebibliography}{9} % or {99}, if there are more than ten references.

\bibitem{LiFaDeMa_2004}
Likhoshvai V.A., Fadeev S.I., Demidenko G.V., Matushkin Yu.G.
Modeling nonbranching multistage synthesis by an equation with retarded argument. Sib. Zh. Ind. Mat. 2004. Vol.~7, no.~1. Pp.~73--94.

\bibitem{De_2012}
Demidenko G.V. Systems of differential equations of higher dimension and delay equations. Siberian Math. J. 2012. Vol.~53, no.~6. Pp.~1021--1028.

\bibitem{DeUv_2016}
Demidenko G.V., Uvarova I.A.
On a class of systems of ordinary differential equations of large dimension.
J. Appl. Industr. Math. 2016. Vol.~10, no.~2. Pp.~179--191.

\end{thebibliography}

%\end{document}