

\iffalse
\documentclass[12pt]{llncs}

\usepackage{todonotes}

\usepackage{nla} 

\begin{document}
\fi

\title{On Estimates for Solutions to \\ a Class of Nonautonomous Systems of Neutral Type \\with Concentrated and Distributed Delays\thanks{The research is supported
by the Russian Science Foundation (grant no.~24-21-00367),
https://rscf.ru/project/24-21-00367/.}}

\author{Inessa I. Matveeva
}
\institute{Novosibirsk State University, Novosibirsk, Russia\\
  \email{i.matveeva@g.nsu.ru}
}

\maketitle

\begin{abstract}
We consider a class of neutral type systems of 
nonautonomous differential equations with concentrated 
and distributed delays. 
Using a Lyapunov--Krasovskii functional, some estimates for solutions 
are established. The obtained estimates allow us to conclude whether the solutions 
are stable. 
\keywords{time-delay systems of neutral type, variable coefficients, 
estimates for solutions, stability, Lyapunov--Krasovskii functional}
\end{abstract}

We consider time-delay systems of the following form:
$$
\frac{d}{dt}y(t) = A(t) y(t) + B(t) y(t-\tau) + C(t) \frac{d}{dt} y(t-\tau)
+ \int\limits^t_{t-\tau}D(t, t-s)y(s)\,ds
$$
$$
+ F\left(t, y(t), y(t-\tau), \frac{d}{dt} y(t-\tau), \int\limits^t_{t-\tau}D(t, t-s)y(s)\,ds \right), 
\qquad 
t \ge 0, 
\eqno(1)
$$
where 
$A(t)$, $B(t)$, $C(t)$, $D(t,s)$
are 
$(n \times n)$-matrices with continuous real-valued entries; i.e.
$$
a_{ij}(t), \ b_{ij}(t), \ c_{ij}(t) \in C(\overline{\mathbb R}_+), 
\quad
d_{ij}(t, s) \in C(\overline{\mathbb R}_+ \times [0, \tau]),
\quad 
i, j = 1, \dots, n,
$$
$\tau > 0$
is a delay,
$F(t, u_1, u_2, u_3, u_4)$ 
is a continuous real-valued vector-function. 
We assume that 
$F(t, u_1, u_2, u_3, u_4)$ 
is a Lipschitz function of 
$u_1$, $u_4$ 
on every compact set 
$G \subset [0,\infty) \times {\mathbb R}^n \times {\mathbb R}^n \times {\mathbb R}^n \times {\mathbb R}^n$ 
and satisfies the inequality
$$
\|F(t, u_1, u_2, u_3, u_4)\| \le q_1 \|u_1\| + q_2 \|u_2\|, 
\qquad
t \ge 0, 
\quad 
u_j \in {\mathbb R}^n,
\quad
q_j \ge 0. 
$$

Using a Lyapunov--Krasovskii functional introduced in [1] and functional difference equations,
we establish some estimates for solutions to these systems. 
The obtained estimates allow us to conclude whether the solutions 
are stable. In the case of the exponential stability, 
stabilization rates of the solutions at infinity are pointed out.
The present work continues our investigations of properties 
of solutions to nonautonomous time-delay systems (see, for example, [2, 3]). 

% At the end of the text, acknowledgments are expressed, if you haven't
% made a footnote from the title. For example, we can write

%The research is supported by the Russian Science Foundation
%(grant no.~24-21-00367), https://rscf.ru/project/24-21-00367/

\begin{thebibliography}{9} % or {99}, if there is more than ten references.

\bibitem{1}
Matveeva I. I. 
Estimates of the exponential decay of solutions to linear systems of 
neutral type with periodic coefficients.  
Journal of Applied and Industrial Mathematics. 2019. Vol. 13, no. 3. Pp. 511--518.

\bibitem{2}
Matveeva I. I.
Estimates for solutions to a class of nonautonomous systems of neutral type 
with unbounded delay. Siberian Mathematical Journal. 2021. Vol. 62, no.~3. Pp. 468--481.

\bibitem{3}
Matveeva I. I.
Estimates for solutions to one class of nonlinear nonautonomous systems with 
time-varying concentrated and distributed delays.   
Siberian Electronic Mathematical Reports. 2021. Vol. 18, no. 2. Pp. 1689--1697.

\end{thebibliography}
%\end{document}
