
\iffalse
\documentclass[12pt]{llncs}

\usepackage{todonotes}

\usepackage{nla} 

\begin{document}
\fi

\title{Estimates for solutions to neutral Type differential equations: applications to the hopfield neural networks model\thanks{The research is supported
by the Russian Science Foundation (grant no.~24-21-00367),
https://rscf.ru/project/24-21-00367/.}}

\author{Maria A. Skvortsova}
\institute{Novosibirsk State University, Novosibirsk, Russia\\
\email{sm-18-nsu@yandex.ru}}

\maketitle

\begin{abstract}
We consider Hopfield neural networks model described by a system of differential equations of neutral type with several delays.
Using Lyapunov--Krasovskii functionals we obtain estimates for solutions
characterizing the stabilization rate at infinity.

\keywords{neutral type differential equations, Hopfield neural networks model, Lyapunov--Krasovskii functionals, estimates for solutions, exponential stability}
\end{abstract}

Consider the following system of differential equations of neutral type
$$
\dot{x}_i(t)=-c_i x_i(t)
+\sum\limits_{j=1}^{n} a_{ij} f_j(x_j(t))
+\sum\limits_{j=1}^{n} b_{ij} g_j(x_j(t-\tau_{ij}(t)))
+\sum\limits_{j=1}^{n} e_{ij} \dot{x}_j(t-\xi_{ij}(t))
+u_i,
$$
$$
i=1,\dots,n, \quad t>0,
$$
where
$\tau_{ij}(t), \ \xi_{ij}(t) \in C^1(\mathbb{R}_{+})$,
$f_j(x), \ g_j(x) \in C(\mathbb{R})$,
and the following conditions hold
$$
0 \leq \xi_{ij}(t) \leq \xi,
\quad
0 \leq \tau_{ij}(t) \leq \tau,
\quad
\dot{\xi}_{ij}(t) \leq \bar{\xi},
\quad
\dot{\tau}_{ij}(t) \leq \bar{\tau},
$$
$$
|f_j(x)-f_j(y)| \leq l_j |x-y|,
\quad
|g_j(x)-g_j(y)| \leq m_j |x-y|,
\quad
x,y \in \mathbb{R}.
$$
This system was considered in~[1] as a model of Hopfield neural networks.
The authors of this work studied the exponential stability of stationary solutions to the system using a quasi-linear Lyapunov--Krasovskii functional.
They obtained sufficient conditions for the coefficients of the system, delay parameters and nonlinear functions, under which the stationary solution is exponentially stable.
The question of obtaining constructive estimates for solutions characterizing the stabilization rate at infinity is also of great interest for this model.

Note that in the present time there exist the results about obtaining constructive estimates for solutions to wide classes of neutral type differential equations (see, for example,~[2--6]).
In these works the authors proposed several quadratic Lyapunov--Krasovskii functionals, which allow to obtain estimates for solutions characterizing the stabilization rate at infinity.

In this paper we discuss how the ideas~[2--6] of constructing Lyapunov--Krasovskii functionals can be applied to the Hopfield neural networks model.

% At the end of the text, acknowledgments are expressed, if you haven't
% made a footnote from the title. For example, we can write

%The research is supported by the Russian Science Foundation
%(grant no.~24-21-00367), https://rscf.ru/project/24-21-00367/

\begin{thebibliography}{9} % or {99}, if there is more than ten references.

\bibitem{WaZhFuZh_2021}
Wan L., Zhou Q., Fu H., Zhang Q.
Exponential stability of Hopfield neural networks of neutral type
with multiple time-varying delays.
AIMS Mathematics.
2021. Vol.~6, no.~8. Pp.~8030--8043.

\bibitem{De_2009}
Demidenko G.V.
Stability of solutions to linear differential equations of neutral type.
Journal of Analysis and Applications.
2009. Vol.~7, no.~3. Pp.~119--130.

\bibitem{DeMa_2014}
Demidenko G.V., Matveeva I.I.
On estimates of solutions to systems of differential equations of neutral
type with periodic coefficients.
Siberian Mathematical Journal.
2014. Vol.~55, no.~5. Pp.~866--881.

\bibitem{Ma_2017}
Matveeva I.I.
On exponential stability of solutions to periodic neutral-type systems.
Siberian Mathematical Journal.
2017. Vol.~58, no.~2. Pp.~264--270.

\bibitem{Ma_2021}
Matveeva I.I.
Estimates for solutions to a class of nonautonomous systems
of neutral type with unbounded delay.
Siberian Mathematical Journal.
2021. Vol.~62, no.~3. Pp.~468--481.

\bibitem{DeMa_2021}
Demidenko G.V., Matveeva I.I.
The second Lyapunov method for time-delay systems.
Functional Differential Equations and Applications
(Editors: Domoshnitsky A., Rasin A., Padhi S.).
Series: Springer Proceedings in Mathematics \& Statistics.
Singapore: Springer Nature, 2021. Vol.~379. Pp.~145--167.

\end{thebibliography}

%\end{document}
